---
title: 'Sentiment Analysis of Game of Thrones'
date: 'created on 27 of march and updated `r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      message = FALSE)

library(tidyverse)
library(here)

# For text mining:

library(pdftools)
library(tidytext)
library(textdata) 
library(ggwordcloud)
```


#1) Downloading Game of thrones pdf-file and extracting text

```{r get-document}
got_path <- here("data","got.pdf")
got_text <- pdf_text(got_path)

```


#2) We want to exclude title page and chapter index from our sentiment analysis, so we want the data set to start from page 6, where the prologue starts, to page 731, the end of the last chapter before the summary of all the houses.

```{r select-pages}
got_page <- got_text[6:731]

head(got_page)
```


#3) Then we turn our pdf into a dataframe, so that we can use it in Tidyverse. Lines in the text is shown with a '\n' and so we have to use the str_split command to seperate each line into its own row


```{r split-lines}
got_df <- data.frame(got_text) %>% 
  mutate(text_full = str_split(got_text, pattern = '\n')) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full)) 

got_df
```


#Now we will make a tidy format of tokens, which are the words using unnest_tokens

```{r Tidy formar-tokens}
got_tokens <- got_df %>% 
  unnest_tokens(word, text_full)
got_tokens

```

#Word Count
```{r count-words}
got_wc <- got_tokens %>% 
  count(word) %>% 
  arrange(-n)
got_wc
```



```{r stopwords}
got_stop <- got_tokens %>% 
  anti_join(stop_words) %>% 
  select(-got_text)
```

Now check the counts again: 
```{r count-words2}
got_swc <- got_stop %>% 
  count(word) %>% 
  arrange(-n)
```

What if we want to get rid of all the numbers (non-text) in `ipcc_stop`?
```{r skip-numbers}
# This code will filter out numbers by asking:
# If you convert to as.numeric, is it NA (meaning those words)?
# If it IS NA (is.na), then keep it (so all words are kept)
# Anything that is converted to a number is removed

got_no_numeric <- got_stop %>% 
  filter(is.na(as.numeric(word)))
got_no_numeric %>% 
  count(word) %>% 
  arrange(-n)
```


# A word cloud of GOT report words (non-numeric)

```{r wordcloud-prep}
# Unique words 
length(unique(got_no_numeric$word))

# Limit word cloud to top 100
got_top100 <- got_no_numeric %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(100)

got_top100
```

```{r wordcloud}
got_cloud <- ggplot(data = got_top100, aes(label = word)) +
  geom_text_wordcloud() +
  theme_minimal()

got_cloud
```


```{r wordcloud-custom}
ggplot(data = got_top100, aes(label = word, size = n)) +
  geom_text_wordcloud_area(aes(color = n)) +
  scale_size_area(max_size = 12) +
  scale_color_gradientn(colors = c("purple","pink","lightblue")) +
  theme_minimal()
```


#Sentiment analysis


```{r afinn}
get_sentiments(lexicon = "afinn")

afinn_pos <- get_sentiments("afinn") %>% 
  filter(value %in% c(3,4,5))

afinn_pos
```

bing: binary, "positive" or "negative"
```{r bing}
get_sentiments(lexicon = "bing")

```


```{r nrc}
get_sentiments(lexicon = "nrc")

```

# Sentiment analysis with afinn: 


```{r bind-afinn}
got_afinn <- got_stop %>% 
  inner_join(get_sentiments("afinn"))
got_afinn
```


```{r count-afinn}
got_afinn_hist <- got_afinn %>% 
  count(value)

# Plot them: 
ggplot(data = got_afinn_hist, aes(x = value, y = n)) +
  geom_col(aes(fill = value)) +
  theme_bw()
```

Investigate some of the words in a bit more depth:
```{r afinn-2}

got_afinn2 <- got_afinn %>% 
  filter(value == 2)
```

```{r afinn-2-more}
# Check the unique 2-score words:
unique(got_afinn2$word)

# Count & plot them, limit to 40 as example
got_afinn2_n <- got_afinn2 %>% 
  count(word, sort = TRUE) %>% 
  mutate(word = fct_reorder(factor(word), n)) %>% 
  head(40)


ggplot(data = got_afinn2_n, aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  theme_bw()

```


#summarize sentiment for the report: 

```{r summarize-afinn}
got_summary <- got_afinn %>% 
  summarize(
    mean_score = mean(value),
    median_score = median(value)
  )
got_summary 
```
 

### NRC lexicon for sentiment analysis

We can use the NRC lexicon to start "binning" text by the feelings they're typically associated with. As above, we'll use inner_join() to combine the IPCC non-stopword text with the nrc lexicon: 

```{r bind-bing}
got_nrc <- got_stop %>% 
  inner_join(get_sentiments("nrc"))
got_nrc
```



```{r check-exclusions}
got_exclude <- got_stop %>% 
  anti_join(get_sentiments("nrc"))

# View(got_exclude)

# Count to find the most excluded:
got_exclude_n <- got_exclude %>% 
  count(word, sort = TRUE)

head(got_exclude_n)
```

**Lesson: always check which words are EXCLUDED in sentiment analysis using a pre-built lexicon! **

Now find some counts: 
```{r count-bing}
got_nrc_n <- got_nrc %>% 
  count(sentiment, sort = TRUE)

# And plot them:

ggplot(data = got_nrc_n, aes(x = sentiment, y = n)) +
  geom_col(aes(fill = sentiment))+
  theme_bw()
```

Or count by sentiment *and* word, then facet:
```{r count-nrc}
got_nrc_n5 <- got_nrc %>% 
  count(word,sentiment, sort = TRUE) %>% 
  group_by(sentiment) %>% 
  top_n(5) %>% 
  ungroup()

got_nrc_gg <- ggplot(data = got_nrc_n5, aes(x = reorder(word,n), y = n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, ncol = 2, scales = "free") +
  coord_flip() +
  theme_minimal() +
  labs(x = "Word", y = "count")

# Show it
got_nrc_gg

# Save it
ggsave(plot = got_nrc_gg, 
       here("figures","got_nrc_sentiment.png"), 
       height = 8, 
       width = 5)

```

#checking words
```{r nrc-confidence}
honor <- get_sentiments(lexicon = "nrc") %>% 
  filter(word == "honor")

# check it out:
honor
```

